---
title: "LanternfliesData"
output: 
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default

---

This R Notebook allows us to test for relationship between bodysize metrics and thermal tolerance. 

Loading all packages:
```{r}
library(tidyverse)
library(car)
```
Importing Data:
```{r}

h1 <- read_csv("/Users/survanisinha/Downloads/Lantern Fly Data Collection _ GSSRP '24 - Hot.csv")
c1 <- read_csv("/Users/survanisinha/Downloads/Lantern Fly Data Collection _ GSSRP '24 - Cold.csv")

```
```{r}
#Separating into male & female data sets

#subset to male data
hotmales <- h1 %>%
  filter(`Sex(M/F)` == 'M') %>%
  select(`ID`, `Length-Nosetoabdomen(mm)`, `Length-NosetoWingtip(mm)`, `AbdomenLength(mm)`, `Weight(g)`, `CTmax(s)`, `Temperature(C)`)

coldmales <- c1 %>%
  filter(`Sex(M/F)` == 'Male') %>%
  select(`ID`, `Length-Nosetoabdomen(mm)`, `Length-NosetoWingtip(mm)`, `AbdomenLength(mm)`, `Weight(g)`, `CTmin(s)`, `Temperature(C)`)

#subset to female data
hotfemales <- h1 %>%
  filter(`Sex(M/F)` == 'F') %>%
  select(`ID`, `Length-Nosetoabdomen(mm)`, `Length-NosetoWingtip(mm)`, `AbdomenLength(mm)`, `Weight(g)`, `CTmax(s)`, `Temperature(C)`)

coldfemales <- c1 %>%
  filter(`Sex(M/F)` == 'Female') %>%
  select(`ID`, `Length-Nosetoabdomen(mm)`, `Length-NosetoWingtip(mm)`, `AbdomenLength(mm)`, `Weight(g)`, `CTmin(s)`, `Temperature(C)`)

coldmales$`CTmin(s)LOG` <- log(coldmales$`CTmin(s)`)
coldfemales$`CTmin(s)LOG` <- log(coldfemales$`CTmin(s)`)

hotmales$`CTmax(s)LOG` <- log(hotmales$`CTmax(s)`)
hotfemales$`CTmax(s)LOG` <- log(hotfemales$`CTmax(s)`)
```
Removing extraneous data:
```{r}
#coldfemales
rowsToRemove <- c(21, 20, 27, 9, 4, 3) 
coldfemalesRowsRemoved <- coldfemales[-rowsToRemove, ]

#coldmales
rowsToRemove <- c(46, 27, 6, 2, 1) 
coldmalesRowsRemoved <- coldmales[-rowsToRemove, ]

#hotfemales
rowsToRemove <- c(2, 3, 4, 8) 
hotfemalesRowsRemoved <- hotfemales[-rowsToRemove, ]

#hotmales
rowsToRemove <- c(2) 
hotmalesRowsRemoved <- hotmales[-rowsToRemove, ]
```
Graph Creating for Entire Data Set:
```{r}
#HOT

#plotting weight vs sex
ggplot(data = h1, mapping = aes(x = `Sex(M/F)`, y = `Weight(g)`)) + geom_boxplot() + geom_jitter(alpha = 0.3, color = "red") + ggtitle("Weight(g) vs Sex(M/F)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Sex (M/F)", y = "Weight (g)")

#plotting CTmax(s) vs sex
ggplot(data = h1, mapping = aes(x = `Sex(M/F)`, y = `CTmax(s)`)) + geom_boxplot() + geom_jitter(alpha = 0.3, color = "red") + ggtitle("CTmax(s) vs Sex(M/F)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Sex (M/F)", y = "CTmax (s)")

#plotting Length-Nosetoabdomen(mm) vs sex
ggplot(data = h1, mapping = aes(x = `Sex(M/F)`, y = `Length-Nosetoabdomen(mm)`)) + geom_boxplot() + geom_jitter(alpha = 0.3, color = "red") + ggtitle("Length-Nose to Abdomen(mm) vs Sex(M/F)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Sex (M/F)", y = "Length from Nose to Abdomen (mm)")

#plotting Length-NosetoWingtip(mm) vs sex
ggplot(data = h1, mapping = aes(x = `Sex(M/F)`, y = `Length-NosetoWingtip(mm)`)) + geom_boxplot() + geom_jitter(alpha = 0.3, color = "red") + ggtitle("Length-Nose to Wingtip(mm) vs Sex(M/F)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Sex (M/F)", y = "Length from Nose to Wingtip (mm)")

#plotting AbdomenLength(mm) vs sex
ggplot(data = h1, mapping = aes(x = `Sex(M/F)`, y = `AbdomenLength(mm)`)) + geom_boxplot() + geom_jitter(alpha = 0.3, color = "red") + ggtitle("Abdomen Length(mm) vs Sex(M/F)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Sex (M/F)", y = "Abdomen Length (mm)")

#plotting Length-Nosetoabdomen(mm) vs AbdomenLength(mm)
ggplot(data = h1, mapping = aes(x = `AbdomenLength(mm)`, y = `Length-Nosetoabdomen(mm)`)) + geom_point(color = "red") + ggtitle("Length-Nose to Abdomen(mm) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Length from Nose to Abdomen (mm)")

#plotting Length-NosetoWingtip(mm) vs AbdomenLength(mm)
ggplot(data = h1, mapping = aes(x = `AbdomenLength(mm)`, y = `Length-NosetoWingtip(mm)`)) + geom_point(color = "red") + ggtitle("Length-Nose to Wingtip(mm) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Length from Nose to Wingtip (mm)")

#plotting Weight(g) vs AbdomenLength(mm)
ggplot(data = h1, mapping = aes(x = `AbdomenLength(mm)`, y = `Weight(g)`)) + geom_point(color = "red") + ggtitle("Weight(g) vs AbdmenLength(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Weight (g)")

#plotting CTmax(s) vs AbdomenLength(mm)
ggplot(data = h1, mapping = aes(x = `AbdomenLength(mm)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("CTmax(s) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "CTmax (s)")

#plotting CTmax(s) vs Weight(g)
ggplot(data = h1, mapping = aes(x = `Weight(g)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("CTmax(s) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "CTmax (s)")

#plotting Length-Nosetoabdomen(mm) vs Weight (g)
ggplot(data = h1, mapping = aes(x = `Weight(g)`, y = `Length-Nosetoabdomen(mm)`)) + geom_point(color = "red") + ggtitle("Length-Nose to Abdomen vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Length from Nose to Abdomen (g)")

#plotting Length-NosetoWingtip(mm) vs Weight (g)
ggplot(data = h1, mapping = aes(x = `Weight(g)`, y = `Length-NosetoWingtip(mm)`)) + geom_point(color = "red") + ggtitle("Length-Nose to Wingtip(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Length from Nose to Wingtip (g)")

#plotting AbdomenLength(mm) vs Weight (g)
ggplot(data = h1, mapping = aes(x = `Weight(g)`, y = `AbdomenLength(mm)`)) + geom_point(color = "red") + ggtitle("Abdomen Length(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Abdomen Length (g)")

#plotting CTmax(s) vs Length-Nosetoabdomen(mm))
ggplot(data = h1, mapping = aes(x = `Length-Nosetoabdomen(mm)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("CTmax(s) vs Length-Nose to Abdomen(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Length from Nose to abdomen (mm)", y = "CTmax (s)")

#plotting CTmax(s) vs Length-NosetoWingtip(mm))
ggplot(data = h1, mapping = aes(x = `Length-NosetoWingtip(mm)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("CTmax(s) vs Length-Nose to Wingtip(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Length from Nose to Wingtip (mm)", y = "CTmax (s)")

#plotting CTmax(s) vs AbdomenLength(mm))
ggplot(data = h1, mapping = aes(x = `AbdomenLength(mm)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("CTmax(s) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "CTmax (s)")

#----

#COLD

#plotting weight vs sex
ggplot(data = c1, mapping = aes(x = `Sex(M/F)`, y = `Weight(g)`)) + geom_boxplot() + geom_jitter(alpha = 0.3, color = "blue") + ggtitle("Weight(g) vs Sex(M/F)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Sex (M/F)", y = "Weight (g)")

#plotting CTmin(s) vs sex
ggplot(data = c1, mapping = aes(x = `Sex(M/F)`, y = `CTmin(s)`)) + geom_boxplot() + geom_jitter(alpha = 0.3, color = "blue") + ggtitle("CTmin(s) vs Sex(M/F)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Sex (M/F)", y = "CTmin (s)")

#plotting Length-Nosetoabdomen(mm) vs sex
ggplot(data = c1, mapping = aes(x = `Sex(M/F)`, y = `Length-Nosetoabdomen(mm)`)) + geom_boxplot() + geom_jitter(alpha = 0.3, color = "blue") + ggtitle("Length-Nose to Abdomen(mm) vs Sex(M/F)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Sex (M/F)", y = "Length from Nose to Abdomen (mm)")

#plotting Length-NosetoWingtip(mm) vs sex
ggplot(data = c1, mapping = aes(x = `Sex(M/F)`, y = `Length-NosetoWingtip(mm)`)) + geom_boxplot() + geom_jitter(alpha = 0.3, color = "blue") + ggtitle("Length-Nose to Wingtip(mm) vs Sex(M/F)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Sex (M/F)", y = "Length from Nose to Wingtip (mm)")

#plotting AbdomenLength(mm) vs sex
ggplot(data = c1, mapping = aes(x = `Sex(M/F)`, y = `AbdomenLength(mm)`)) + geom_boxplot() + geom_jitter(alpha = 0.3, color = "blue") + ggtitle("Abdomen Length(mm) vs Sex(M/F)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Sex (M/F)", y = "Abdomen Length (mm)")

#plotting Length-Nosetoabdomen(mm) vs AbdomenLength(mm)
ggplot(data = c1, mapping = aes(x = `AbdomenLength(mm)`, y = `Length-Nosetoabdomen(mm)`)) + geom_point(color = "blue") + ggtitle("Length-Nose to Abdomen(mm) vs AbdomenLength(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Length from Nose to Abdomen (mm)")

#plotting Length-NosetoWingtip(mm) vs AbdomenLength(mm)
ggplot(data = c1, mapping = aes(x = `AbdomenLength(mm)`, y = `Length-NosetoWingtip(mm)`)) + geom_point(color = "blue") + ggtitle("Length-Nose to Wingtip(mm) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Length from Nose to Wingtip (mm)")

#plotting Weight(g) vs AbdomenLength(mm)
ggplot(data = c1, mapping = aes(x = `AbdomenLength(mm)`, y = `Weight(g)`)) + geom_point(color = "blue") + ggtitle("Weight(g) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Weight(g)")

#plotting CTmin(s) vs AbdomenLength(mm)
ggplot(data = c1, mapping = aes(x = `AbdomenLength(mm)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("CTmin(s) vs Abdomen Length (mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "CTmin (s)")

#plotting CTmin(s) vs Weight(g)
ggplot(data = c1, mapping = aes(x = `Weight(g)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("CTmin(s) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "CTmin (s)")

#plotting Length-Nosetoabdomen(mm) vs Weight (g)
ggplot(data = c1, mapping = aes(x = `Weight(g)`, y = `Length-Nosetoabdomen(mm)`)) + geom_point(color = "blue") + ggtitle("Length-Nose to Abdomen(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Length from Nose to Abdomen (g)")

#plotting Length-NosetoWingtip(mm) vs Weight (g)
ggplot(data = c1, mapping = aes(x = `Weight(g)`, y = `Length-NosetoWingtip(mm)`)) + geom_point(color = "blue") + ggtitle("Length-Nose to Wingtip(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Length from Nose to Wingtip (g)")

#plotting AbdomenLength(mm) vs Weight (g)
ggplot(data = c1, mapping = aes(x = `Weight(g)`, y = `AbdomenLength(mm)`)) + geom_point(color = "blue") + ggtitle("Abdomen Length(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Abdomen Length (g)")

#plotting CTmin(s) vs Length-Nosetoabdomen(mm))
ggplot(data = c1, mapping = aes(x = `Length-Nosetoabdomen(mm)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("CTmin(s) vs Length-Nose to Abdomen(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Length from Nose to abdomen (mm)", y = "CTmin (s)")

#plotting CTmin(s) vs Length-NosetoWingtip(mm))
ggplot(data = c1, mapping = aes(x = `Length-NosetoWingtip(mm)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("CTmin(s) vs Length-Nose to Wingtip(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Length from Nose to Wingtip (mm)", y = "CTmin (s)")

#plotting CTmin(s) vs AbdomenLength(mm)
ggplot(data = c1, mapping = aes(x = `AbdomenLength(mm)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("CTmin(s) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "CTmin (s)")
```
Graphing based on sex:
```{r}
#HOT

#females

# #plotting Length-Nosetoabdomen(mm) vs AbdomenLength(mm)
# ggplot(data = hotfemales, mapping = aes(x = `AbdomenLength(mm)`, y = `Length-Nosetoabdomen(mm)`)) + geom_point(color = "red") + ggtitle("Hot Female: Length-Nose to Abdomen(mm) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Length from Nose to Abdomen (mm)")
# 
# #plotting Length-NosetoWingtip(mm) vs AbdomenLength(mm)
# ggplot(data = hotfemales, mapping = aes(x = `AbdomenLength(mm)`, y = `Length-NosetoWingtip(mm)`)) + geom_point(color = "red") + ggtitle("Hot Female: Length-Nose to Wingtip(mm) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Length from Nose to Wingtip (mm)")
# 
# #plotting Weight(g) vs AbdomenLength(mm)
# ggplot(data = hotfemales, mapping = aes(x = `AbdomenLength(mm)`, y = `Weight(g)`)) + geom_point(color = "red") + ggtitle("Hot Female: Weight(g) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Weight(g)")

#plotting CTmax(s) vs AbdomenLength(mm)
ggplot(data = hotfemalesRowsRemoved, mapping = aes(x = `AbdomenLength(mm)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("Hot Female: CTmax(s) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "CTmax (s)")

#plotting CTmax(s) vs Weight(g)
ggplot(data = hotfemalesRowsRemoved, mapping = aes(x = `Weight(g)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("Hot Female: CT max(s) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "CTmax (s)")

# #plotting Length-Nosetoabdomen(mm) vs Weight (g)
# ggplot(data = hotfemales, mapping = aes(x = `Weight(g)`, y = `Length-Nosetoabdomen(mm)`)) + geom_point(color = "red") + ggtitle("Hot Female: Length-Nose to Abdomen(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Length from Nose to Abdomen (g)")
# 
#plotting Length-NosetoWingtip(mm) vs Weight (g)
ggplot(data = hotfemalesRowsRemoved, mapping = aes(x = `Weight(g)`, y = `Length-NosetoWingtip(mm)`)) + geom_point(color = "red") + ggtitle("Hot Female: Length-Nose to Wingtip (mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Length from Nose to Wingtip (g)")

# #plotting AbdomenLength(mm) vs Weight (g)
# ggplot(data = hotfemales, mapping = aes(x = `Weight(g)`, y = `AbdomenLength(mm)`)) + geom_point(color = "red") + ggtitle("Hot Female: Abdomen Length(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Abdomen Length (g)")

#plotting CTmax(s) vs Length-Nosetoabdomen(mm))
ggplot(data = hotfemalesRowsRemoved, mapping = aes(x = `Length-Nosetoabdomen(mm)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("Hot Female: CTmax(s) vs Length-Nose to Abdomen(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Length from Nose to abdomen (mm)", y = "CTmax (s)")

#plotting CTmax(s) vs Length-NosetoWingtip(mm))
ggplot(data = hotfemalesRowsRemoved, mapping = aes(x = `Length-NosetoWingtip(mm)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("Hot Female: CTmax(s) vs Length-Nose to Wingtip(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Length from Nose to Wingtip (mm)", y = "CTmax (s)")

#plotting CTmax(s) vs AbdomenLength(mm))
ggplot(data = hotfemalesRowsRemoved, mapping = aes(x = `AbdomenLength(mm)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("Hot Female: CTmax(s) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "CTmax (s)")

# #box plot for distribution of CTmax 
# ggplot(data = h1, mapping = aes(x = `ID`, y = `CTmax(s)`)) + geom_boxplot() + geom_jitter(alpha = 0.3, color = "red") + ggtitle("CTmax(s) vs Lanternflies") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "ID", y = "CTmax(s)")

#males


# #plotting Length-Nosetoabdomen(mm) vs AbdomenLength(mm)
# ggplot(data = hotmales, mapping = aes(x = `AbdomenLength(mm)`, y = `Length-Nosetoabdomen(mm)`)) + geom_point(color = "red") + ggtitle("Hot Male: Length-Nose to Abdomen(mm) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Length from Nose to Abdomen (mm)")
# 
# #plotting Length-NosetoWingtip(mm) vs AbdomenLength(mm)
# ggplot(data = hotmales, mapping = aes(x = `AbdomenLength(mm)`, y = `Length-NosetoWingtip(mm)`)) + geom_point(color = "red") + ggtitle("Hot Male: Length-Nose to Wingtip(mm) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Length from Nose to Wingtip (mm)")
# 
# #plotting Weight(g) vs AbdomenLength(mm)
# ggplot(data = hotmales, mapping = aes(x = `AbdomenLength(mm)`, y = `Weight(g)`)) + geom_point(color = "red") + ggtitle("Hot Male: Weight(g) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Weight(g)")

#plotting CTmax(s) vs AbdomenLength(mm)
ggplot(data = hotmalesRowsRemoved, mapping = aes(x = `AbdomenLength(mm)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("Hot Male: CTmax(s) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "CTmax (s)")

#plotting CTmax(s) vs Weight(g)
ggplot(data = hotmalesRowsRemoved, mapping = aes(x = `Weight(g)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("Hot Male: CTmax(s) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "CTmax (s)")

# #plotting Length-Nosetoabdomen(mm) vs Weight (g)
# ggplot(data = hotmales, mapping = aes(x = `Weight(g)`, y = `Length-Nosetoabdomen(mm)`)) + geom_point(color = "red") + ggtitle("Hot Male: Length-Nose to Abdomen(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Length from Nose to Abdomen (g)")
# 
#plotting Length-NosetoWingtip(mm) vs Weight (g)
ggplot(data = hotmalesRowsRemoved, mapping = aes(x = `Weight(g)`, y = `Length-NosetoWingtip(mm)`)) + geom_point(color = "red") + ggtitle("Hot Male: Length-Nose to Wingtip(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Length from Nose to Wingtip (g)")

# #plotting AbdomenLength(mm) vs Weight (g)
# ggplot(data = hotmales, mapping = aes(x = `Weight(g)`, y = `AbdomenLength(mm)`)) + geom_point(color = "red") + ggtitle("Hot Male: Abdomen Length(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Abdomen Length (g)")

#plotting CTmax(s) vs Length-Nosetoabdomen(mm))
ggplot(data = hotmalesRowsRemoved, mapping = aes(x = `Length-Nosetoabdomen(mm)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("Hot Male: CTmax(s) vs Length-Nose to Abdomen(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Length from Nose to abdomen (mm)", y = "CTmax (s)")

#plotting CTmax(s) vs Length-NosetoWingtip(mm))
ggplot(data = hotmalesRowsRemoved, mapping = aes(x = `Length-NosetoWingtip(mm)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("Hot Male: CTmax(s) vs Length-Nose to Wingtip(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Length from Nose to Wingtip (mm)", y = "CTmax (s)")

#plotting CTmax(s) vs AbdomenLength(mm))
ggplot(data = hotmalesRowsRemoved, mapping = aes(x = `AbdomenLength(mm)`, y = `CTmax(s)`)) + geom_point(color = "red") + ggtitle("Hot Male: CTmax(s) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="red", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "CTmax (s)")

#----

#COLD

#females

# #plotting Length-Nosetoabdomen(mm) vs AbdomenLength(mm)
# ggplot(data = coldfemales, mapping = aes(x = `AbdomenLength(mm)`, y = `Length-Nosetoabdomen(mm)`)) + geom_point(color = "blue") + ggtitle("Cold Female: Length-Nose to Abdomen(mm) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Length from Nose to Abdomen (mm)")
# 
# #plotting Length-NosetoWingtip(mm) vs AbdomenLength(mm)
# ggplot(data = coldfemales, mapping = aes(x = `AbdomenLength(mm)`, y = `Length-NosetoWingtip(mm)`)) + geom_point(color = "blue") + ggtitle("Cold Female: Length-Nose to Wingtip(mm) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Length from Nose to Wingtip (mm)")
# 
# #plotting Weight(g) vs AbdomenLength(mm)
# ggplot(data = coldfemales, mapping = aes(x = `AbdomenLength(mm)`, y = `Weight(g)`)) + geom_point(color = "blue") + ggtitle("Cold Female: Weight(g) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Weight(g)")

#plotting CTmin(s) vs AbdomenLength(mm)
ggplot(data = coldfemalesRowsRemoved, mapping = aes(x = `AbdomenLength(mm)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("Cold Female: CTmin(s) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "CTmin (s)")

#plotting CTmin(s) vs Weight(g)
ggplot(data = coldfemalesRowsRemoved, mapping = aes(x = `Weight(g)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("Cold Female: CTmin(s) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "CTmin (s)")

# #plotting Length-Nosetoabdomen(mm) vs Weight (g)
# ggplot(data = coldfemales, mapping = aes(x = `Weight(g)`, y = `Length-Nosetoabdomen(mm)`)) + geom_point(color = "blue") + ggtitle("Cold Female: Length-Nose to Abdomen(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Length from Nose to Abdomen (g)")
# 
#plotting Length-NosetoWingtip(mm) vs Weight (g)
ggplot(data = coldfemalesRowsRemoved, mapping = aes(x = `Weight(g)`, y = `Length-NosetoWingtip(mm)`)) + geom_point(color = "blue") + ggtitle("Cold Female: Length-Nose to Wingtip(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Length from Nose to Wingtip (g)")

# #plotting AbdomenLength(mm) vs Weight (g)
# ggplot(data = coldfemales, mapping = aes(x = `Weight(g)`, y = `AbdomenLength(mm)`)) + geom_point(color = "blue") + ggtitle("Cold Female: Abdomen Length(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Abdomen Length (g)")

#plotting CTmin(s) vs Length-Nosetoabdomen(mm))
ggplot(data = coldfemalesRowsRemoved, mapping = aes(x = `Length-Nosetoabdomen(mm)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("Cold Female: CTmin(s) vs Length-Nose to Abdomen(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Length from Nose to abdomen (mm)", y = "CTmin (s)")

#plotting CTmin(s) vs Length-NosetoWingtip(mm))
ggplot(data = coldfemalesRowsRemoved, mapping = aes(x = `Length-NosetoWingtip(mm)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("Cold Female: CTmin(s) vs Length-Nose to Wingtip(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Length from Nose to Wingtip (mm)", y = "CTmin (s)")

#plotting CTmin(s) vs AbdomenLength(mm))
ggplot(data = coldfemalesRowsRemoved, mapping = aes(x = `AbdomenLength(mm)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("Cold Female: CTmin(s) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "CTmin (s)")

#males

# #plotting Length-Nosetoabdomen(mm) vs AbdomenLength(mm)
# ggplot(data = coldmales, mapping = aes(x = `AbdomenLength(mm)`, y = `Length-Nosetoabdomen(mm)`)) + geom_point(color = "blue") + ggtitle("Cold Male: Length-Nose to Abdomen(mm) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Length from Nose to Abdomen (mm)")
# 
# #plotting Length-NosetoWingtip(mm) vs AbdomenLength(mm)
# ggplot(data = coldmales, mapping = aes(x = `AbdomenLength(mm)`, y = `Length-NosetoWingtip(mm)`)) + geom_point(color = "blue") + ggtitle("Cold Male: Length-Nose to Wingtip(mm) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Length from Nose to Wingtip (mm)")
# 
# #plotting Weight(g) vs AbdomenLength(mm)
# ggplot(data = coldmales, mapping = aes(x = `AbdomenLength(mm)`, y = `Weight(g)`)) + geom_point(color = "blue") + ggtitle("Cold Male: Weight(g) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "Weight(g)")

#plotting CTmin(s) vs AbdomenLength(mm)
ggplot(data = coldmalesRowsRemoved, mapping = aes(x = `AbdomenLength(mm)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("Cold Male: CTmin(s) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "CTmin (s)")

#plotting CTmin(s) vs Weight(g)
ggplot(data = coldmalesRowsRemoved, mapping = aes(x = `Weight(g)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("Cold Male: CTmin(s) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "CTmin (s)")

# #plotting Length-Nosetoabdomen(mm) vs Weight (g)
# ggplot(data = coldmales, mapping = aes(x = `Weight(g)`, y = `Length-Nosetoabdomen(mm)`)) + geom_point(color = "blue") + ggtitle("Cold Male: Length-Nose to Abdomen(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Length from Nose to Abdomen (g)")
# 
#plotting Length-NosetoWingtip(mm) vs Weight (g)
ggplot(data = coldmalesRowsRemoved, mapping = aes(x = `Weight(g)`, y = `Length-NosetoWingtip(mm)`)) + geom_point(color = "blue") + ggtitle("Cold Male: Length-Nose to Wingtip(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Length from Nose to Wingtip (g)")

# #plotting AbdomenLength(mm) vs Weight (g)
# ggplot(data = coldmales, mapping = aes(x = `Weight(g)`, y = `AbdomenLength(mm)`)) + geom_point(color = "blue") + ggtitle("Cold Male: Abdomen Length(mm) vs Weight(g)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Weight (g)", y = "Abdomen Length (g)")

#plotting CTmin(s) vs Length-Nosetoabdomen(mm)
ggplot(data = coldmalesRowsRemoved, mapping = aes(x = `Length-Nosetoabdomen(mm)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("Cold Male: CTmin(s) vs Length-Nose to Abdomen(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Length from Nose to abdomen (mm)", y = "CTmin (s)")

#plotting CTmin(s) vs Length-NosetoWingtip(mm)
ggplot(data = coldmalesRowsRemoved, mapping = aes(x = `Length-NosetoWingtip(mm)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("Cold Male: CTmin(s) vs Length-Nose to Wingtip(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Length from Nose to Wingtip (mm)", y = "CTmin (s)")

#plotting CTmin(s) vs AbdomenLength(mm)
ggplot(data = coldmalesRowsRemoved, mapping = aes(x = `AbdomenLength(mm)`, y = `CTmin(s)`)) + geom_point(color = "blue") + ggtitle("Cold Male: CTmin(s) vs Abdomen Length(mm)") + theme(plot.title = element_text(hjust = 0.5, color="blue", size=14, face="bold.italic")) + labs(x = "Abdomen Length (mm)", y = "CTmin (s)")

```
Summary Stats:
```{r}
nrow(coldmalesRowsRemoved)
nrow(hotmalesRowsRemoved)
nrow(coldfemalesRowsRemoved)
nrow(hotfemalesRowsRemoved)
```
Running Linear Models on relationship between WEIGHT and CTmin/max:
```{r}
# HotFemaleWeightlm <- lm(`CTmax(s)` ~ `Weight(g)`, data = hotfemalesRowsRemoved)
# summary(HotFemaleWeightlm)
# 
# HotMaleWeightlm <- lm(`CTmax(s)` ~ `Weight(g)`, data = hotmalesRowsRemoved)
# summary(HotMaleWeightlm)
# 
# ColdFemaleWeightlm <- lm(`CTmin(s)` ~ `Weight(g)`, data = coldfemalesRowsRemoved)
# summary(ColdFemaleWeightlm)
# 
# ColdMaleWeightlm <- lm(`CTmin(s)` ~ `Weight(g)`, data = coldmalesRowsRemoved)
# summary(ColdMaleWeightlm)
#----
HotFemaleWeightlmLOG <- lm(`CTmax(s)LOG` ~ `Weight(g)`, data = hotfemalesRowsRemoved)
summary(HotFemaleWeightlmLOG)

HotMaleWeightlmLOG <- lm(`CTmax(s)LOG` ~ `Weight(g)`, data = hotmalesRowsRemoved)
summary(HotMaleWeightlmLOG)

ColdFemaleWeightlmLOG <- lm(`CTmin(s)LOG` ~ `Weight(g)`, data = coldfemalesRowsRemoved)
summary(ColdFemaleWeightlmLOG)

ColdMaleWeightlmLOG <- lm(`CTmin(s)LOG` ~ `Weight(g)`, data = coldmalesRowsRemoved)
summary(ColdMaleWeightlmLOG)
```
Checking Regression Assumptions for relationship between WEIGHT and CTmin/max:
```{r}
plot(HotFemaleWeightlmLOG, 1, main = "Hot Female between Weight and CTmax(LOG)")
plot(HotMaleWeightlmLOG, 1, main = "Hot Male between Weight and CTmax(LOG)")
plot(ColdFemaleWeightlmLOG, 1, main = "Cold Female between Weight and CTmin(LOG)")
plot(ColdMaleWeightlmLOG, 1, main = "Cold Male between Weight and CTmin(LOG)")

plot(HotFemaleWeightlmLOG, 3, main = "Hot Female between Weight and CTmax(LOG)")
plot(HotMaleWeightlmLOG, 3, main = "Hot Male between Weight and CTmax(LOG)")
plot(ColdFemaleWeightlmLOG, 3, main = "Cold Female between Weight and CTmin(LOG)")
plot(ColdMaleWeightlmLOG, 3, main = "Cold Male between Weight and CTmin(LOG)")

qqnorm(hotfemalesRowsRemoved$`CTmax(s)LOG`, main = "Q-Q Plot of CTmax for Hot Females (LOG)")
qqline(hotfemalesRowsRemoved$`CTmax(s)LOG`, col = "darkorchid4", lwd = 2)

qqnorm(hotmalesRowsRemoved$`CTmax(s)LOG`, main = "Q-Q Plot of CTmax for Hot Males (LOG)")
qqline(hotmalesRowsRemoved$`CTmax(s)LOG`, col = "darkorchid4", lwd = 2)

qqnorm(coldfemalesRowsRemoved$`CTmin(s)LOG`, main = "Q-Q Plot of CTmin for Cold Females (LOG)")
qqline(coldfemalesRowsRemoved$`CTmin(s)LOG`, col = "darkorchid4", lwd = 2)

qqnorm(coldmalesRowsRemoved$`CTmin(s)LOG`, main = "Q-Q Plot of CTmin for Cold Males (LOG)")
qqline(coldmalesRowsRemoved$`CTmin(s)LOG`, col = "darkorchid4", lwd = 2)

```
Running Linear Models on relationship between LENGTH-NOSETOWINGTIP and CTmin/max:
```{r}
HotFemaleLengthNosetoWingtiplm <- lm(`CTmax(s)` ~ `Length-NosetoWingtip(mm)`, data = hotfemalesRowsRemoved)
summary(HotFemaleLengthNosetoWingtiplm)

HotMaleLengthNosetoWingtiplm <- lm(`CTmax(s)` ~ `Length-NosetoWingtip(mm)`, data = hotmalesRowsRemoved)
summary(HotMaleLengthNosetoWingtiplm)

ColdFemaleLengthNosetoWingtiplm <- lm(`CTmin(s)` ~ `Length-NosetoWingtip(mm)`, data = coldfemalesRowsRemoved)
summary(ColdFemaleLengthNosetoWingtiplm)

ColdMaleLengthNosetoWingtiplm <- lm(`CTmin(s)` ~ `Length-NosetoWingtip(mm)`, data = coldmalesRowsRemoved)
summary(ColdMaleLengthNosetoWingtiplm)

#-----
print('LOG adjusted:')

HotFemaleLengthNosetoWingtiplmLOG <- lm(`CTmax(s)LOG` ~ `Length-NosetoWingtip(mm)`, data = hotfemalesRowsRemoved)
summary(HotFemaleLengthNosetoWingtiplmLOG)

HotMaleLengthNosetoWingtiplmLOG <- lm(`CTmax(s)LOG` ~ `Length-NosetoWingtip(mm)`, data = hotmalesRowsRemoved)
summary(HotMaleLengthNosetoWingtiplmLOG)

ColdFemaleLengthNosetoWingtiplmLOG <- lm(`CTmin(s)LOG` ~ `Length-NosetoWingtip(mm)`, data = coldfemalesRowsRemoved)
summary(ColdFemaleLengthNosetoWingtiplmLOG)

ColdMaleLengthNosetoWingtiplmLOG <- lm(`CTmin(s)LOG` ~ `Length-NosetoWingtip(mm)`, data = coldmalesRowsRemoved)
summary(ColdMaleLengthNosetoWingtiplmLOG)
```
Checking Regression Assumptions for relationship between LENGTH-NOSETOWINGTIP and CTmin/max:
```{r}
# plot(HotFemaleLengthNosetoWingtiplm, 1, main = "Hot Female")
# plot(HotMaleLengthNosetoWingtiplm, 1, main = "Hot Male")
# plot(ColdFemaleLengthNosetoWingtiplm, 1, main = "Cold Female")
# plot(ColdMaleLengthNosetoWingtiplm, 1, main = "Cold Male")
# 
# plot(HotFemaleLengthNosetoWingtiplm, 3, main = "Hot Female")
# plot(HotMaleLengthNosetoWingtiplm, 3, main = "Hot Male")
# plot(ColdFemaleLengthNosetoWingtiplm, 3, main = "Cold Female")
# plot(ColdMaleLengthNosetoWingtiplm, 3, main = "Cold Male")
# 
# qqnorm(hotfemalesRowsRemoved$`CTmax(s)`, main = "Q-Q Plot of CTmax for Hot Females")
# qqline(hotfemalesRowsRemoved$`CTmax(s)`, col = "steelblue", lwd = 2)
# 
# qqnorm(hotmalesRowsRemoved$`CTmax(s)`, main = "Q-Q Plot of CTmax for Hot Males")
# qqline(hotmalesRowsRemoved$`CTmax(s)`, col = "steelblue", lwd = 2)
# 
# qqnorm(coldfemalesRowsRemoved$`CTmin(s)`, main = "Q-Q Plot of CTmin for Cold Females")
# qqline(coldfemalesRowsRemoved$`CTmin(s)`, col = "steelblue", lwd = 2)
# 
# qqnorm(coldmalesRowsRemoved$`CTmin(s)`, main = "Q-Q Plot of CTmin for Cold Males")
# qqline(coldmalesRowsRemoved$`CTmin(s)`, col = "steelblue", lwd = 2)

#----
print("LOG adjusted")

plot(HotFemaleLengthNosetoWingtiplmLOG, 1, main = "Hot Female (LOG)")
plot(HotMaleLengthNosetoWingtiplmLOG, 1, main = "Hot Male (LOG)")
plot(ColdFemaleLengthNosetoWingtiplmLOG, 1, main = "Cold Female (LOG)")
plot(ColdMaleLengthNosetoWingtiplmLOG, 1, main = "Cold Male (LOG)")

plot(HotFemaleLengthNosetoWingtiplmLOG, 3, main = "Hot Female (LOG)")
plot(HotMaleLengthNosetoWingtiplmLOG, 3, main = "Hot Male (LOG)")
plot(ColdFemaleLengthNosetoWingtiplmLOG, 3, main = "Cold Female (LOG)")
plot(ColdMaleLengthNosetoWingtiplmLOG, 3, main = "Cold Male (LOG)")

qqnorm(hotfemalesRowsRemoved$`CTmax(s)LOG`, main = "Q-Q Plot of CTmax for Hot Females (LOG)")
qqline(hotfemalesRowsRemoved$`CTmax(s)LOG`, col = "darkorchid4", lwd = 2)

qqnorm(hotmalesRowsRemoved$`CTmax(s)LOG`, main = "Q-Q Plot of CTmax for Hot Males (LOG)")
qqline(hotmalesRowsRemoved$`CTmax(s)LOG`, col = "darkorchid4", lwd = 2)

qqnorm(coldfemalesRowsRemoved$`CTmin(s)LOG`, main = "Q-Q Plot of CTmin for Cold Females (LOG)")
qqline(coldfemalesRowsRemoved$`CTmin(s)LOG`, col = "darkorchid4", lwd = 2)

qqnorm(coldmalesRowsRemoved$`CTmin(s)LOG`, main = "Q-Q Plot of CTmin for Cold Males (LOG)")
qqline(coldmalesRowsRemoved$`CTmin(s)LOG`, col = "darkorchid4", lwd = 2)
```
Running Linear Models on relationship between ABDOMEN LENGTH and CTmin/max:
```{r}
HotFemaleAbdomenlm <- lm(`CTmax(s)` ~ `AbdomenLength(mm)`, data = hotfemalesRowsRemoved)
summary(HotFemaleAbdomenlm)

HotMaleAbdomenlm <- lm(`CTmax(s)` ~ `AbdomenLength(mm)`, data = hotmalesRowsRemoved)
summary(HotMaleAbdomenlm)

ColdFemaleAbdomenlm <- lm(`CTmin(s)` ~ `AbdomenLength(mm)`, data = coldfemalesRowsRemoved)
summary(ColdFemaleAbdomenlm)

ColdMaleAbdomenlm <- lm(`CTmin(s)` ~ `AbdomenLength(mm)`, data = coldmalesRowsRemoved)
summary(ColdMaleAbdomenlm)

#----

HotFemaleAbdomenlmLOG <- lm(`CTmax(s)LOG` ~ `AbdomenLength(mm)`, data = hotfemalesRowsRemoved)
summary(HotFemaleAbdomenlmLOG)

HotMaleAbdomenlmLOG <- lm(`CTmax(s)LOG` ~ `AbdomenLength(mm)`, data = hotmalesRowsRemoved)
summary(HotMaleAbdomenlmLOG)

ColdFemaleAbdomenlmLOG <- lm(`CTmin(s)LOG` ~ `AbdomenLength(mm)`, data = coldfemalesRowsRemoved)
summary(ColdFemaleAbdomenlmLOG)

ColdMaleAbdomenlmLOG <- lm(`CTmin(s)LOG` ~ `AbdomenLength(mm)`, data = coldmalesRowsRemoved)
summary(ColdMaleAbdomenlmLOG)
```
Checking Regression Assumptions for relationship between ABDOMEN LENGTH and CTmin/max:
```{r}
plot(HotFemaleAbdomenlm, 1)
plot(HotMaleAbdomenlm, 1)
plot(ColdFemaleAbdomenlm, 1)
plot(ColdMaleAbdomenlm, 1)

plot(HotFemaleAbdomenlm, 3)
plot(HotMaleAbdomenlm, 3)
plot(ColdFemaleAbdomenlm, 3)
plot(ColdMaleAbdomenlm, 3)

qqnorm(hotfemalesRowsRemoved$`CTmax(s)`)
qqline(hotfemalesRowsRemoved$`CTmax(s)`, col = "steelblue", lwd = 2)

qqnorm(hotmalesRowsRemoved$`CTmax(s)`)
qqline(hotmalesRowsRemoved$`CTmax(s)`, col = "steelblue", lwd = 2)

qqnorm(coldfemalesRowsRemoved$`CTmin(s)`)
qqline(coldfemalesRowsRemoved$`CTmin(s)`, col = "steelblue", lwd = 2)

qqnorm(coldmalesRowsRemoved$`CTmin(s)`)
qqline(coldmalesRowsRemoved$`CTmin(s)`, col = "steelblue", lwd = 2)

#---

plot(HotFemaleAbdomenlmLOG, 1)
plot(HotMaleAbdomenlmLOG, 1)
plot(ColdFemaleAbdomenlmLOG, 1)
plot(ColdMaleAbdomenlmLOG, 1)

plot(HotFemaleAbdomenlmLOG, 3)
plot(HotMaleAbdomenlmLOG, 3)
plot(ColdFemaleAbdomenlmLOG, 3)
plot(ColdMaleAbdomenlmLOG, 3)

qqnorm(hotfemalesRowsRemoved$`CTmax(s)LOG`)
qqline(hotfemalesRowsRemoved$`CTmax(s)LOG`, col = "darkorchid4", lwd = 2)

qqnorm(hotmalesRowsRemoved$`CTmax(s)LOG`)
qqline(hotmalesRowsRemoved$`CTmax(s)LOG`, col = "darkorchid4", lwd = 2)

qqnorm(coldfemalesRowsRemoved$`CTmin(s)LOG`)
qqline(coldfemalesRowsRemoved$`CTmin(s)LOG`, col = "darkorchid4", lwd = 2)

qqnorm(coldmalesRowsRemoved$`CTmin(s)LOG`)
qqline(coldmalesRowsRemoved$`CTmin(s)LOG`, col = "darkorchid4", lwd = 2)
```
Running Linear Models on relationship between LENGTH-NOSETOABDOMEN and CTmin/max:
```{r}
HotFemaleLengthNosetoAbdomenlmLOG <- lm(`CTmax(s)LOG` ~ `Length-Nosetoabdomen(mm)`, data = hotfemalesRowsRemoved)
summary(HotFemaleLengthNosetoAbdomenlmLOG)

HotMaleLengthNosetoAbdomenlmLOG <- lm(`CTmax(s)LOG` ~ `Length-Nosetoabdomen(mm)`, data = hotmalesRowsRemoved)
summary(HotMaleLengthNosetoAbdomenlmLOG)

ColdFemaleLengthNosetoAbdomenlmLOG <- lm(`CTmin(s)LOG` ~ `Length-Nosetoabdomen(mm)`, data = coldfemalesRowsRemoved)
summary(ColdFemaleLengthNosetoAbdomenlmLOG)

ColdMaleLengthNosetoAbdomenlmLOG <- lm(`CTmin(s)LOG` ~ `Length-Nosetoabdomen(mm)`, data = coldmalesRowsRemoved)
summary(ColdMaleLengthNosetoAbdomenlmLOG)
```
Checking Regression Assumptions for relationship between LENGTH-NOSETOABDOMEN and CTmin/max:
```{r}
plot(HotFemaleLengthNosetoAbdomenlmLOG, 1, main = "Hot Female Length from Nose to Abdomen compared to CTmax(LOG)")
plot(HotMaleLengthNosetoAbdomenlmLOG, 1, main = "Hot Male Length from Nose to Abdomen compared to CTmax(LOG)")
plot(ColdFemaleLengthNosetoAbdomenlmLOG, 1, main = "Cold Female Length from Nose to Abdomen compared to CTmin(LOG)")
plot(ColdMaleLengthNosetoAbdomenlmLOG, 1, main = "Cold Male Length from Nose to Abdomen compared to CTmin(LOG)")

plot(HotFemaleLengthNosetoAbdomenlmLOG, 3, main = "Hot Female Length from Nose to Abdomen compared to CTmax(LOG)")
plot(HotMaleLengthNosetoAbdomenlmLOG, 3, main = "Hot Male Length from Nose to Abdomen compared to CTmax(LOG)")
plot(ColdFemaleLengthNosetoAbdomenlmLOG, 3, main = "Cold Female Length from Nose to Abdomen compared to CTmin(LOG)")
plot(ColdMaleLengthNosetoAbdomenlmLOG, 3, main = "Cold Male Length from Nose to Abdomen compared to CTmin(LOG)")

qqnorm(hotfemalesRowsRemoved$`CTmax(s)LOG`, main = "Q-Q Plot of CTmax for Hot Females (LOG)")
qqline(hotfemalesRowsRemoved$`CTmax(s)LOG`, col = "darkorchid4", lwd = 2)

qqnorm(hotmalesRowsRemoved$`CTmax(s)LOG`, main = "Q-Q Plot of CTmax for Hot Males (LOG)")
qqline(hotmalesRowsRemoved$`CTmax(s)LOG`, col = "darkorchid4", lwd = 2)

qqnorm(coldfemalesRowsRemoved$`CTmin(s)LOG`, main = "Q-Q Plot of CTmin for Cold Females (LOG)")
qqline(coldfemalesRowsRemoved$`CTmin(s)LOG`, col = "darkorchid4", lwd = 2)

qqnorm(coldmalesRowsRemoved$`CTmin(s)LOG`, main = "Q-Q Plot of CTmin for Cold Males (LOG)")
qqline(coldmalesRowsRemoved$`CTmin(s)LOG`, col = "darkorchid4", lwd = 2)
```
Graphing Weight vs CTmin/max LOG transformed with Regression Lines:
```{r}
#Hot

#plotting hot females: CTmax (log) vs Weight
model <- lm(`CTmax(s)LOG` ~ `Weight(g)`, data = hotfemalesRowsRemoved)
summary(model)
intercept <- coef(model)[1]
slope <- coef(model)[2]
equation <- paste("y =", round(intercept, 2), "+", round(slope, 2), "* x")
p_value_text <- expression(paste(italic("p"), " = ", 0.0769))
  
ggplot(data = hotfemalesRowsRemoved, mapping = aes(x = `Weight(g)`, y = `CTmax(s)LOG`)) + geom_point(color = "deeppink2") + geom_smooth(method = "lm", color = "red", se = FALSE) + ggtitle("Female Time to CT max (s)") + theme(plot.title = element_text(hjust = 0.5, color="black", size=18, face="bold"), axis.title.x = element_text(size = 16), axis.title.y = element_text(size = 16), axis.text.x = element_text(size = 14),axis.text.y = element_text(size = 14)) + labs(x = "Weight (g)", y = "Time to CTmax (s) (log)") + annotate("text", x = Inf, y = Inf, label = equation, hjust = 1.1, vjust = 1.5, color = "black", size = 5) + annotate("text", x = Inf, y = Inf, label = p_value_text, hjust = 1.1, vjust = 4.2, color = "black", size = 5)

#plotting hot males: CTmax (log) vs Weight
model <- lm(`CTmax(s)LOG` ~ `Weight(g)`, data = hotmalesRowsRemoved)
summary(model)
intercept <- coef(model)[1]
slope <- coef(model)[2]
equation <- paste("y =", round(intercept, 2), "+", round(slope, 2), "* x")
p_value_text <- expression(paste(italic("p"), " = ", 0.246))

ggplot(data = hotmalesRowsRemoved, mapping = aes(x = `Weight(g)`, y = `CTmax(s)LOG`)) + geom_point(color = "forestgreen") + geom_smooth(method = "lm", color = "red", se = FALSE) + ggtitle("Male Time to CT max (s)") + theme(plot.title = element_text(hjust = 0.5, color="black", size=18, face="bold"), axis.title.x = element_text(size = 16), axis.title.y = element_text(size = 16), axis.text.x = element_text(size = 14),axis.text.y = element_text(size = 14)) + labs(x = "Weight (g)", y = "Time to CTmax (s) (log)") + annotate("text", x = Inf, y = Inf, label = equation, hjust = 1.1, vjust = 1.5, color = "black", size = 5) + annotate("text", x = Inf, y = Inf, label = p_value_text, hjust = 1.1, vjust = 4.2, color = "black", size = 5)

#Cold

#plotting cold females: CTmin (log) vs Weight
model <- lm(`CTmin(s)LOG` ~ `Weight(g)`, data = coldfemalesRowsRemoved)
summary(model)
intercept <- coef(model)[1]
slope <- coef(model)[2]
equation <- paste("y =", round(intercept, 2), "+", round(slope, 2), "* x")
p_value_text <- expression(paste(italic("p"), " = ", 4.59e-09))

ggplot(data = coldfemalesRowsRemoved, mapping = aes(x = `Weight(g)`, y = `CTmin(s)LOG`)) + geom_point(color = "deeppink2") + geom_smooth(method = "lm", color = "blue", se = FALSE) + ggtitle("Female Time to CT min (s)") + theme(plot.title = element_text(hjust = 0.5, color="black", size=18, face="bold"), axis.title.x = element_text(size = 16), axis.title.y = element_text(size = 16), axis.text.x = element_text(size = 14),axis.text.y = element_text(size = 14)) + labs(x = "Weight (g)", y = "Time to CTmin (s) (log)") + annotate("text", x = Inf, y = Inf, label = equation, hjust = 1.1, vjust = 1.5, color = "black", size = 5) + annotate("text", x = Inf, y = Inf, label = p_value_text, hjust = 1.1, vjust = 4.2, color = "black", size = 5)

#plotting cold males: CTmin (log) vs Weight
model <- lm(`CTmin(s)LOG` ~ `Weight(g)`, data = coldmalesRowsRemoved)
summary(model)
intercept <- coef(model)[1]
slope <- coef(model)[2]
equation <- paste("y =", round(intercept, 2), "+", round(slope, 2), "* x")
p_value_text <- expression(paste(italic("p"), " = ", 0.00754))

ggplot(data = coldmalesRowsRemoved, mapping = aes(x = `Weight(g)`, y = `CTmin(s)LOG`)) + geom_point(color = "forestgreen") + geom_smooth(method = "lm", color = "blue", se = FALSE) + ggtitle("Male Time to CT min (s)") + theme(plot.title = element_text(hjust = 0.5, color="black", size=18, face="bold"), axis.title.x = element_text(size = 16), axis.title.y = element_text(size = 16), axis.text.x = element_text(size = 14),axis.text.y = element_text(size = 14)) + labs(x = "Weight (g)", y = "Time to CTmin (s) (log)") + annotate("text", x = Inf, y = Inf, label = equation, hjust = 1.1, vjust = 1.5, color = "black", size = 5) + annotate("text", x = Inf, y = Inf, label = p_value_text, hjust = 1.1, vjust = 4.2, color = "black", size = 5)
```

